### 2021-11-24 sections/awards.tex
Update awards.tex

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College at the University of Oxford Book and Travel Grants} 
{Allowances for books and conference participation (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
{Oxford, UK}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ACCP Winter School Scholarship}
{Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
{Montevideo, Uruguay}
{ 2015}
\end{cvhonors}

>>>>

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md

@@

\begin{cvhonors}
\cvhonor
{St Hilda's College Travel Grant} 
{Allowances for conference participation in the USA, {\pounds} 950} 
{Oxford, UK}
{2022}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{St Hilda's College Muriel Wise Fund and Book Grant} 
{Research grant for the training of machine learning algorithms, DPhil (PhD) project data storage, and allowances for books, {\pounds} 530} 
{Oxford, UK}
{2021}
\end{cvhonors}

\begin{cvhonors}
\cvhonor
{St Hilda's College Travel and Book Grants} 
{Allowances for conference participation in Portugal and books (travel grant was declined because of coronavirus pandemic), {\pounds} 745} 
{Oxford, UK}
{2020}
\end{cvhonors}

@@

\begin{cvhonors}
\cvhonor
{ACCP Winter School Scholarship}
{Financial support for the Winter School in Methods and Data Analysis at the Universidad Cat\'olica de Uruguay, awarded by the Chilean Political Science Association (ACCP), {\pounds} 300}
{Montevideo, URY}
{ 2015}
\end{cvhonors}
